Consistent Polyhedral Surrogates via Embedding

### 2019-07-27 notes/top-k.tex
Finished writing up Bayes Risk section

\subsection{Bayes Risk}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\subsection{Bayes Risk}
First, consider the case where $u_y = 0$ and $u'_y = 1$, where $u_j = u'_j \forall i \neq j$.
Note that $y \in \{t+1, \ldots, n\}$.
As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.

So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
\jessie{Fix the two-line situation here...}
\begin{align*}
1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq 1 + \ubar' - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
- \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq \frac{1}{k} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
-p_y \frac{k+1}{k} u_y &\leq \frac{1}{k} - p_y \frac{k+1}{k} u'_y \\
0 &\leq \frac{1}{k} - p_y \frac{k+1}{k}\\
p_y &\leq \frac{1}{k+1}
\end{align*}

Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.

\begin{align*}
1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u} &\leq 1 + \ubar' - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u'}\\
\frac{1}{k}- \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} &\leq \frac{1+\epsilon}{k} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u'}\\
\frac{1}{k}- p_y(1 + \frac{1}{k}) &\leq \frac{1+\epsilon}{k} - p_y(1 + \epsilon + \frac{1}{k})\\
0 &\leq \frac{\epsilon}{k} - p_y(\epsilon)\\
p_y \leq \frac 1 k
\end{align*}
In this case, $u_y=1$ is preferable to $u+y >1$.
If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but are restricted to $u_y \leq \ubar_{-y} + 1$.
Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
However, we can construct $u$ as given below.

\begin{conjecture}
	Fix $p \in \simplex$.
	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
	The property \[\gamma(p) = 
	\left[
	\begin{cases*}
	0 & p_i \leq \frac {1}{k+1}\\
	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
	\frac{g_b}{k - g_t} + \frac{k-1}{k-g_t} & o/w
	\end{cases*}
	\right]_{i=1}^n
	\] refines the property $\prop{L^{top-k}}$.
\end{conjecture}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
